Work for revision of ``Local Spectral Clustering of Density Upper Level Sets''

### 2021-01-13 notes/weekly_notes/11.19.20.NotesForWeek.tex

\documentclass[11pt,twoside]{article}
\usepackage[preprint]{jmlr2e}
\usepackage{color}
\usepackage{fancyhdr}
\usepackage{amsfonts,epsfig,graphicx}
\usepackage{afterpage}
\usepackage{amsmath,amssymb} 
% \usepackage{fullpage}
\usepackage{epsf} 
\usepackage{graphics} 
\usepackage{amsfonts,amsmath}
% \usepackage[sort,numbers]{natbib} 
\usepackage{psfrag,xspace}
\usepackage{color,etoolbox}

\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-6cm}
\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-4cm}
\addtolength{\textheight}{-1.1\headheight}
\addtolength{\textheight}{-\headsep}
\addtolength{\textheight}{-\footskip}
\setlength{\oddsidemargin}{0.5cm}
\setlength{\evensidemargin}{0.5cm}
\renewcommand{\floatpagefraction}{.8}%

%\newtheorem{theorem}{Theorem} 
%\newtheorem{lemma}{Lemma}
%\newtheorem{proposition}{Proposition}
%\newtheorem{corollary}{Corollary}
%\theoremstyle{definition}
%\newtheorem{definition}{Definition}
%\newtheorem{remark}{Remark}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\usepackage{microtype}
\usepackage{graphicx}
\usepackage{float}
\usepackage[export]{adjustbox}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{xcolor}
%\usepackage{xr-hyper}
%\usepackage{hyperref}
%\usepackage[reqno]{amsmath}
%\usepackage{amsfonts, amsthm, amssymb}
\usepackage{algorithm}
\usepackage{algorithmic}
%\usepackage[parfill]{parskip}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{bm}
\usepackage{mathtools}

%%%%%% Begin Alden

\newcommand{\diam}{\rho}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\left\{#1\right\}_{n \in \mathbb{N}}}
\newcommand{\defeq}{\overset{\mathrm{def}}{=}}
\newcommand{\vol}{\mathrm{vol}}
\newcommand{\cut}{\mathrm{cut}}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Rd}{\Reals^d}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\usepackage{bbm}
\newcommand{\1}{\mathbbm{1}}
\newcommand{\Phibf}{\Phi_{u}}
\newcommand{\Psibf}{\Psi_{u}}
\newcommand{\taubf}{\tau_{u}}
\newcommand{\dist}{\mathrm{dist}}
\newcommand{\Err}{\mathrm{Err}}
\newcommand{\TV}{\mathrm{TV}}

%%% Vectors (no bold font)
\newcommand{\pbf}{p}        % removed bold font
\newcommand{\qbf}{q}
\newcommand{\ebf}[1]{{e}_{#1}}
\newcommand{\pibf}{\pi}

%%% Matrices (no bold font)
\newcommand{\Abf}{A}       % removed bold font 
\newcommand{\Xbf}{X}             
\newcommand{\Wbf}{W}
\newcommand{\Lbf}{L}
\newcommand{\Dbf}{D}
\newcommand{\Ibf}[1]{I_{#1}}

%%% Probability distributions (and related items)
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Cbb}{\mathbb{C}}
\newcommand{\Ebb}{\mathbb{E}}

%%% Sets
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\Sset}{\mathcal{S}}
\newcommand{\Cset}{\mathcal{C}}
\newcommand{\Aset}{\mathcal{A}}
\newcommand{\Asig}{\Aset_{\sigma}}
\newcommand{\Csig}{\Cset_{\sigma}}
\newcommand{\Asigr}{\Aset_{\sigma,\sigma + r}}
\newcommand{\Csigr}{\Cset_{\sigma,\sigma + r}}

%%% Graph quantities
\newcommand{\Cest}{\widehat{C}}
\newcommand{\degminpr}{d_{\min}'}
\newcommand{\degminwt}{\widetilde{d}_{\min}}
\newcommand{\degmaxwt}{\widetilde{d}_{\max}}
\newcommand{\degmax}{d_{\max}}
\newcommand{\piminwt}{\widetilde{\pi}_{\min}}
\newcommand{\piminpr}{\pibf_{\min}'}
\newcommand{\degmin}{d_{\min}}

%%% Operators
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\dx}{\,dx}
\newcommand{\dy}{\,dy}
\newcommand{\dt}{\,dt}

%%% Algorithm notation
\newcommand{\ppr}{{\sc PPR}}
\newcommand{\pprspace}{{\sc PPR~}}

%%% Tilde notation for quantities over the expansion set 
\newcommand{\wt}[1]{\widetilde{#1}}
\newcommand{\wn}{\widetilde{n}}
\newcommand{\wX}{\widetilde{\Xbf}}
\newcommand{\wx}{\widetilde{x}}
\newcommand{\wz}{\widetilde{z}}
\newcommand{\wbz}{\widetilde{\bf{z}}}
\newcommand{\wu}{\widetilde{u}}
\newcommand{\wPbb}{\widetilde{\Pbb}}
\newcommand{\wf}{\widetilde{f}}
\newcommand{\wDbf}{\widetilde{\Dbf}}
\newcommand{\piwt}{\widetilde{\pi}}

\newcommand{\sbcomment}[1]{{\color{red} \bf{{{{SB --- #1}}}}}}
\newcommand{\ag}[1]{\textcolor{red}{#1}}

%\newtheoremstyle{aldenthm}
%{6pt} % Space above
%{6pt} % Space below
%{\itshape} % Body font
%{} % Indent amount
%{\bfseries} % Theorem head font
%{.} % Punctuation after theorem head
%{.5em} % Space after theorem head
%{} % Theorem head spec (can be left empty, meaning `normal')

%\theoremstyle{aldenthm}
%\newtheorem{theorem}{Theorem}
%\newtheorem{definition}{Definition}
%\newtheorem{lemma}{Lemma}
%\newtheorem{proposition}{Proposition}
%\newtheorem{corollary}{Corollary}

%\newtheoremstyle{aldenrmrk}
%{6pt} % Space above
%{6pt} % Space below
%{} % Body font
%{} % Indent amount
%{\itshape} % Theorem head font
%{.} % Punctuation after theorem head
%{.5em} % Space after theorem head
%{} % Theorem head spec (can be left empty, meaning `normal')
%
%\theoremstyle{aldenrmrk}
%\newtheorem{remark}{Remark}
%%%%%% End Alden

%\title{Local Spectral Clustering of Density Upper Level Sets}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.
%
%\author{
%Alden Green \And
%Sivaraman Balakrishnan \And
%Ryan J. Tibshirani}
%
%\begin{document}
%\maketitle
%
%\vspace{0.1in}
%\begin{abstract}

\newcommand{\widgraph}[2]{\includegraphics[keepaspectratio,width=#1]{#2}}
\newcommand{\Like}{\ensuremath{\mathcal{L}}}
\newcommand{\Ball}[2]{\mathbb{B}_{#1}(#2)}
\newcommand{\Complement}[1]{\overline{#1}}

\newcommand{\xsam}{\ensuremath{x}}
\newcommand{\samind}{\ensuremath{\ell}}
\newcommand{\Xrv}{\ensuremath{X}}
\newcommand{\Event}{\ensuremath{\mathcal{E}}}
\newcommand{\Fevent}{\ensuremath{\mathcal{F}}}

\newcommand{\usedim}{\ensuremath{d}}
\newcommand{\mubold}{\ensuremath{\boldsymbol{\mu}}}
\newcommand{\lambold}{\ensuremath{\boldsymbol{\lambda}}}
\newcommand{\sep}{\ensuremath{\xi}}
\newcommand{\mixind}{\ensuremath{i}}
\newcommand{\mixtwo}{\ensuremath{j}}
\newcommand{\nummix}{\ensuremath{M}}
\newcommand{\mustar}{\ensuremath{\mu^*}}
\newcommand{\muboldstar}{\ensuremath{\mubold^*}}
\newcommand{\muboldt}{\ensuremath{\mubold^t}}

\newcommand{\numobs}{\ensuremath{n}}
\newcommand{\SamLike}{\ensuremath{\Like_\numobs}}
\newcommand{\PopLike}{\ensuremath{\Like}}
\newcommand{\Exs}{\E}
\newcommand{\thetanew}{\ensuremath{\theta^{\text{\small{new}} }}}

\newcommand{\stepsize}{\ensuremath{s}}

\newcommand{\QMAT}{\ensuremath{\mathbf{Q}}} 
\newcommand{\DMAT}{\ensuremath{\mathbf{D}}}

\newcommand{\defn}{\ensuremath{: \, =}}
\newcommand{\muboldtilde}{\ensuremath{\tilde{\mubold}}}

%%% New version of \caption puts things in smaller type, single-spaced 
%%% and indents them to set them off more from the text.
\makeatletter
\long\def\@makecaption#1#2{
        \vskip 0.8ex
        \setbox\@tempboxa\hbox{\small {\bf #1:} #2}
        \parindent 1.5em  %% How can we use the global value of this???
        \dimen0=\hsize
        \advance\dimen0 by -3em
        \ifdim \wd\@tempboxa >\dimen0
                \hbox to \hsize{
                        \parindent 0em
                        \hfil 
                        \parbox{\dimen0}{\def\baselinestretch{0.96}\small
                                {\bf #1.} #2
                                %%\unhbox\@tempboxa
                                } 
                        \hfil}
        \else \hbox to \hsize{\hfil \box\@tempboxa \hfil}
        \fi
        }
\makeatother

\ShortHeadings{Local Spectral Clustering of Density Level Sets}{Green, Balakrishnan and Tibshirani}
\firstpageno{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{Local Spectral Clustering of Density Upper Level Sets}

\author{\name Alden Green \email ajgreen@stat.cmu.edu \\
	\addr Department of Statistics and Data Science\\
	Carnegie Mellon University\\
	Pittsburgh, PA 15213
	\AND
	\name Sivaraman Balakrishnan \email sbalakri@stat.cmu.edu \\
	\addr Department of Statistics and Data Science\\
	Carnegie Mellon University\\
	Pittsburgh, PA 15213
	\AND
	Ryan J. Tibshirani \email ryantibs@stat.cmu.edu \\
	\addr Department of Statistics and Data Science\\
	Carnegie Mellon University\\
	Pittsburgh, PA 15213}

\maketitle

\begin{abstract}
We analyze the Personalized PageRank (PPR) algorithm, a local spectral method
for clustering, which extracts clusters using locally-biased random walks around
a given seed node.  In contrast to previous work, we adopt a classical
statistical learning setup, where we obtain samples from an unknown
distribution, and aim to identify connected regions of high-density (density
clusters).  We prove that PPR, run on a neighborhood graph, extracts
sufficiently salient density clusters, that satisfy a set of natural geometric
conditions. We also show a converse result, that PPR can fail to recover
geometrically poorly-conditioned density clusters, even asymptotically. Finally,
we provide empirical support for our theory.
\end{abstract}

\begin{keywords}
	graphs, spectral clustering, density clustering, Personalized PageRank, unsupervised learning
\end{keywords}

\section{Introduction}
\label{sec: introduction}

In this paper, we consider the problem of clustering: splitting a given data set
into groups that satisfy some notion of within-group similarity and
between-group difference.  Our particular focus is on spectral clustering
methods, a family of powerful nonparametric clustering algorithms. Roughly
speaking, a spectral algorithm first constructs a geometric graph $G$, where
vertices correspond to samples, and edges correspond to proximities between
samples. The algorithm then estimates a feature embedding based on (an
appropriate) Laplacian matrix of $G$, and applies a simple clustering technique
(like $k$-means clustering) in the embedded feature space.

When applied to geometric graphs built from a large number of samples, global
spectral clustering methods can be computationally cumbersome and insensitive to
the local geometry of the underlying distribution
\citep{leskovec2010,mahoney2012}.  This has led to increased interest in
\emph{local} spectral clustering algorithms, which leverage locally-biased
spectra computed using random walks around some user-specified seed node.  A
popular local clustering algorithm is the Personalized PageRank (PPR) algorithm,
first introduced by \citet{haveliwala2003}, and then further developed by
several others
\citep{spielman2011,spielman2014,andersen2006,mahoney2012,zhu2013}.

Local spectral clustering techniques have been practically very successful
\citep{leskovec2010,andersen2012,gleich2012,mahoney2012,wu2012}, which has led
many authors to develop supporting theory
\citep{spielman2013,andersen2009,gharan2012,zhu2013} that gives worst-case
guarantees on traditional graph-theoretic notions of cluster quality (such as
conductance).  In this paper, we adopt a classical statistical viewpoint, and
examine what the output of local clustering on a data set reveals about the
underlying density $f$ of the samples.  In particular, we examine the ability of
PPR to recover \emph{density clusters} of $f$, defined as the connected
components of the upper level set $\{x \in \Rd : f(x) \geq \lambda\}$ for some
$\lambda > 0$ (an object of central interest in the statistical clustering
literature, dating back to the work of \citet{hartigan1981}).

\section{Background and related work}

We begin by providing some standard background on the PPR algorithm
and the density clustering setup, before turning our attention to related work
and a detailed summary of our contributions.

\subsection{PPR on a neighborhood graph}

Let $\Xbf = \{x_1,\ldots, x_n\}$ be a sample drawn i.i.d.\ from a distribution
$\Pbb$ on $\Rd$, with density $f$.  For a radius $r > 0$, we define
$G_{n,r}=(V,E)$ to be the \emph{$r$-neighborhood graph} of $\Xbf$, an
unweighted, undirected graph with vertices $V=\Xbf$, and an edge $(x_i,x_j) \in
E$ if and only if $\norm{x_i - x_j} \leq r$, where $\norm{\cdot}$ is the
Euclidean norm. We denote by $\Abf \in \Reals^{n \times n}$ the adjacency
matrix, with entries $\Abf_{uv} = 1$ if $(u,v) \in E$ and $0$ otherwise.  We
also denote by $\Dbf$ the diagonal degree matrix, with entries $\Dbf_{uu} :=
\sum_{v \in V} \Abf_{uv}$, and by $\Ibf{}$ the $n \times n$ identity matrix.

First, we define the PPR vector $\pbf_v = \pbf(v,\alpha;G_{n,r})$, based on 
a given seed node $v \in V$ and a teleportation parameter $\alpha \in [0,1]$, to
be the solution of the following linear system:
\begin{equation}
\label{eqn: ppr_vector}
\pbf_v = \alpha \ebf{v} + (1 - \alpha) \pbf_v \Wbf,
\end{equation}
where $\Wbf = (\Ibf{} + \Dbf^{-1}\Abf)/2$ is the lazy random walk matrix over
$G_{n,r}$ and $e_{v}$ is the indicator vector for node $v$ (that has a 1 in
position $v$ and 0 elsewhere).

%\subsubsection{Sweep cut}
%\label{subsection: sweep_cut}
Next, we define a \emph{$\beta$-sweep cut} of $\pbf_v = (\pbf_v(u))_{u \in V}$,
for a given level $\beta > 0$, as    
\begin{equation}
\label{eqn: sweep_cuts}
S_{\beta,v} := \set{u \in V: \frac{\pbf_v(u)}{\Dbf_{uu}} > \beta}.
\end{equation}
We will use the normalized cut metric to determine which sweep cut $S_{\beta}$
is the best cluster estimate. For a set $S \subseteq V$ with complement $S^c = V
\setminus S$, we define \smash{$\cut(S;G_{n,r}) := \sum_{u \in S, v \in S^c}
\Abf_{uv}$}, and \smash{$\vol(S; G_{n,r}) := \sum_{u \in S} \Dbf_{uu}$}.  We
then define the \emph{normalized cut} of $S$ as
\begin{equation}
\label{eqn: normalized_cut}
\Phi(S; G_{n,r}) := \frac{\cut(S;G_{n,r})}{\min \set{\vol(S; G_{n,r}), \vol(S^c; G_{n,r})}}.
\end{equation}
Having computed sweep cuts $S_{\beta}$ over \smash{$\beta \in (L, U)$} (where
the range $(L,U)$ is user-specified), we output the cluster estimate
\smash{$\Cest = S_{\beta^*}$} with minimum normalized cut.  For concreteness,
the PPR algorithm is summarized in Algorithm~\ref{alg: ppr}.

\begin{algorithm}
\caption{PPR on a neighborhood graph}
\label{alg: ppr}	
{\bfseries Input:} data $\Xbf=\{x_1,\ldots,x_n\}$, radius $r > 0$, teleportation
parameter $\alpha \in [0,1]$, seed $v \in \Xbf$, sweep cut range $(L,U)$. \\     
{\bfseries Output:} cluster estimate $\Cest \subseteq V$.
\begin{algorithmic}[1]
  \STATE Form the neighborhood graph $G_{n,r}$.
  \STATE Compute the PPR vector $\pbf_v=\pbf(v, \alpha; G_{n,r})$ as in
  \eqref{eqn: ppr_vector}.  
  \STATE For \smash{$\beta \in (L,U)$}, compute sweep cuts $S_{\beta}$ as in
  \eqref{eqn: sweep_cuts}. 
  \STATE Return the cluster \smash{$\Cest = S_{\beta^*}$}, where  
  $$
  \beta^* = \argmin_{\beta \in (L,U)}~ \Phi(S_{\beta}; G_{n,r}).
  $$
\end{algorithmic}
\end{algorithm}

\subsection{Estimation of density clusters}

Let \smash{$\Cbb_f(\lambda)$} denote the connected components of the density
upper level set $\{x \in \Rd: f(x) > \lambda\}$.  For a given density cluster
\smash{$\Cset \in \Cbb_f(\lambda)$}, we call $\Cset[\Xbf] = \Cset \cap \Xbf$ the
\emph{empirical density cluster}. The size of the symmetric set difference
between estimated and empirical cluster is a commonly used metric to quantify
cluster estimation error \citep{korostelev1993,polonik1995,rigollet2009}. We
will consider a related metric, the volume of the symmetric set difference,
which weights points according to their degree in $G_{n,r}$. To keep things simple, for a given set $S \subseteq \Xbf$ we write $\vol_{n,r}(S) := \vol(S;G_{n,r})$. 
\begin{definition}
  \label{def:volume_symmetric_set_difference}
  For an estimator \smash{$\Cest \subseteq \Xbf$} and a set 
  $\mathcal{S} \subseteq \Rd$, their symmetric set difference is 
  $$
  \Cest \vartriangle \mathcal{S}[\Xbf] :=
    \bigl(\Cest \setminus \mathcal{S}[\Xbf]\bigr) \cup
    \bigl(\mathcal{S}[\Xbf] \setminus \Cest\bigr).
  $$
  Furthermore, we denote the volume of the symmetric set difference by 
  $$
  \Delta(\Cest, \mathcal{S}[\Xbf]) := \vol_{n,r}(\Cest \vartriangle \mathcal{S}[\Xbf]). 
  $$
\end{definition}

Note that the symmetric set difference does not measure whether \smash{$\Cest$}
can (perfectly) distinguish any two distinct clusters \smash{$\Cset,\Cset' \in 
  \Cbb_f(\lambda)$}. We therefore also study a second notion of cluster 
estimation, first introduced by \citet{hartigan1981}, and defined
asymptotically.

\begin{definition}
  \label{def: consistent_density_cluster_estimation}
  For an estimator \smash{$\Cest \subseteq \Xbf$} and cluster \smash{$\Cset \in
    \Cbb_f(\lambda)$}, we call \smash{$\Cest$} \emph{consistent} for
  \smash{$\Cset$} if for all \smash{$\Cset' \in \Cbb_f(\lambda)$} with  
  \smash{$\Cset \not= \Cset'$}, the following holds as $n \to \infty$: 
  \begin{equation}
    \label{eqn: consistent_density_cluster_recovery}
    \Cset[\Xbf] \subseteq \Cest \quad \text{and} \quad
    \Cest \cap \Cset'[\Xbf] = \emptyset,
  \end{equation}
  with probability tending to 1.
\end{definition}

Consistent cluster recovery roughly ensures that, for a given 
threshold $\lambda>0$, the estimated cluster \smash{$\Cest$} contains all points
in a true density cluster $\Cset \in \Cbb_f(\lambda)$, and simultaneously does 
not contain any points in any other density cluster $\Cset' \in
\Cbb_f(\lambda)$.

With these definitions in place, our broad goal will be to understand the extent
to which the PPR algorithm is able to recover a cluster which either guarantees
a low symmetric set difference to a true density cluster, or which consistently
estimates a true density cluster.

\subsection{Related work}

In addition to the background on local spectral clustering given above, a
few related lines of work are worth highlighting. In the stochastic block model
(SBM), arguably one of the simplest models of network formation, edges between
nodes independently occur with probability based on a latent community
membership. In the SBM, the ability of spectral algorithms to perform
clustering---or community detection---is well-understood, dating 
back to \citet{mcsherry2001} who gives conditions under which the entire
community structure can be recovered. In more recent work, \citet{rohe2011}
upper bound the fraction of nodes misclassified by a spectral algorithm for the
high-dimensional (large number of blocks) SBM, and \citet{lei2015} extend these
results to the sparse (low average degree) regime. Relatedly,
\citet{clauset08,balakrishnan2011,li2018}, analyze the misclassification rate
when the block model exhibits some hierarchical structure. The framework we
consider, in which nodes correspond to data points sampled from an underlying 
density, and edges between nodes are formed based on geometric proximity, is
quite different than the SBM, and therefore so is our analysis.

In general, the study of spectral algorithms on neighborhood graphs has been
focused on establishing asymptotic convergence of eigenvalues and eigenvectors
of certain sample objects to the eigenvalues and eigenfunctions of corresponding
limiting operators. \citet{koltchinskii2000} establish convergence of spectral
projections of the adjacency matrix to a limiting integral operator, with
similar results obtained using simplified proofs in
\citet{rosasco10}. \citet{vonluxburg2008} studies convergence of eigenvectors of
the Laplacian matrix for a neighborhood of fixed radius. \citet{belkin07} and
\citet{garciatrillos18} extend these results to the regime where the radius $r
\to 0$ as $n \to \infty$.

These results are of fundamental importance; however, the behavior of the
spectra of these continuum operators can in general be hard to grasp. Therefore,
further work relating this spectra to the geometry of the underlying
distribution $\Pbb$ is of interest. In this spirit,
\citet{shi2009,schiebinger2015,garciatrillos19} examine the ability of spectral
algorithms to recover the latent labels in certain geometrically
well-conditioned nonparametric mixture models. Their results focus on global
rather than local methods, and thus impose global rather than local conditions
on the nature of the density. Moreover, they do not in general guarantee
recovery of density clusters, which is the focus in our work. Perhaps most
importantly, these works rely on general cluster saliency conditions, which
implicitly depend on many distinct geometric aspects of the cluster $\Cset$
under consideration. We make this dependence more explicit, and in doing so
expose the role each geometric condition plays in the clustering problem.

>>>>

\documentclass{report}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{fullpage}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{tikz}

\usepackage{natbib}
\renewcommand{\bibname}{REFERENCES}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}

\DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
\DeclareFontShape{U}{mathx}{m}{n}{<-> mathx10}{}
\DeclareSymbolFont{mathx}{U}{mathx}{m}{n}
\DeclareMathAccent{\wb}{0}{mathx}{"73}

\DeclarePairedDelimiterX{\norm}[1]{\lVert}{\rVert}{#1}

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\Xsetistiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\ext}[1]{\widetilde{#1}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\Xsetotp}[2]{\langle #1, #2 \rangle}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Xsetiam}{\mathrm{diam}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\vol}{\mathrm{vol}}
\newcommand{\spansp}{\mathrm{span}~}
\newcommand{\1}{\mathbf{1}}

\newcommand{\Linv}{L^{\Xsetagger}}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\argmax}{argmax}

\newcommand{\emF}{\mathbb{F}_n}
\newcommand{\emG}{\mathbb{G}_n}
\newcommand{\emP}{\mathbb{P}_n}
\newcommand{\F}{\mathcal{F}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Rd}{\Reals^d}
\newcommand{\Nbb}{\mathbb{N}}

%%% Vectors
\newcommand{\thetast}{\theta^{\star}}
\newcommand{\betap}{\beta^{(p)}}
\newcommand{\betaq}{\beta^{(q)}}
\newcommand{\vardeltapq}{\varDelta^{(p,q)}}

%%% Matrices
\newcommand{\X}{X} % no bold
\newcommand{\Y}{Y} % no bold
\newcommand{\Z}{Z} % no bold
\newcommand{\Lgrid}{L_{\grid}}
\newcommand{\Xsetgrid}{D_{\grid}}
\newcommand{\Linvgrid}{L_{\grid}^{\Xsetagger}}
\newcommand{\Lap}{{\bf L}}
\newcommand{\NLap}{{\bf N}}
\newcommand{\PLap}{{\bf P}}

%%% Sets and classes
\newcommand{\Xset}{\mathcal{X}}
\newcommand{\Sset}{\mathcal{S}}
\newcommand{\Hclass}{\mathcal{H}}
\newcommand{\Pclass}{\mathcal{P}}
\newcommand{\Leb}{L}
\newcommand{\mc}[1]{\mathcal{#1}}

%%% Distributions and related quantities
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Ebb}{\mathbb{E}}
\newcommand{\Qbb}{\mathbb{Q}}
\newcommand{\Ibb}{\mathbb{I}}

%%% Operators
\newcommand{\Tadj}{T^{\star}}
\newcommand{\Xsetive}{\mathrm{div}}
\newcommand{\Xsetif}{\mathop{}\!\mathrm{d}}
\newcommand{\gradient}{\mathcal{D}}
\newcommand{\Hessian}{\mathcal{D}^2}
\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
\newcommand{\Dotp}[2]{\Bigl\langle #1, #2 \Bigr\rangle}

%%% Misc
\newcommand{\grid}{\mathrm{grid}}
\newcommand{\critr}{R_n}
\newcommand{\Xsetx}{\,dx}
\newcommand{\Xsety}{\,dy}
\newcommand{\Xsetr}{\,dr}
\newcommand{\Xsetxpr}{\,dx'}
\newcommand{\Xsetypr}{\,dy'}
\newcommand{\wt}[1]{\widetilde{#1}}
\newcommand{\wh}[1]{\widehat{#1}}
\newcommand{\ol}[1]{\overline{#1}}
\newcommand{\spec}{\mathrm{spec}}
\newcommand{\LE}{\mathrm{LE}}
\newcommand{\LS}{\mathrm{LS}}
\newcommand{\OS}{\mathrm{OS}}
\newcommand{\PLS}{\mathrm{PLS}}
\newcommand{\dist}{\mathrm{dist}}

%%% Order of magnitude
\newcommand{\soom}{\sim}

% \newcommand{\span}{\textrm{span}}

\newtheoremstyle{alden}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{alden}

\newtheoremstyle{aldenthm}
{6pt} % Space above
{6pt} % Space below
{\itshape} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

\theoremstyle{aldenthm}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}{Remark}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\theoremstyle{remark}

\begin{document}
\title{Work for revision of ``Local Spectral Clustering of Density Upper Level Sets''}
\author{Alden Green}
\date{\today}
\maketitle

\chapter{Lower bound for conductance of continuous-space ball walk}
For $x \in \mc{C}_{\sigma}$ and measurable $\Sset \subseteq \mc{C}_{\sigma}$, let $\ell_{\nu,r}(x) = \nu(B(x,r) \cap \mc{C}_{\sigma})$ and ${J}_{\nu,r}(\mc{S}) = \int_{\mc{S}} \ell_{\nu,r}(x) \,dx$. Further define
\begin{equation*}
\widetilde{P}_{\nu,r}(x; \Sset) := \frac{\nu(\Sset \cap B(x,r))}{\nu(\mc{C}_{\sigma} \cap B(x,r))}, \quad \widetilde{\pi}_{\nu,r}(\Sset) = \frac{J_{\nu,r}(\mc{S})}{J_{\nu,r}(\mc{C}_{\sigma})}, \quad  \widetilde{Q}_{\nu,r}(\Sset_1,\Sset_2) := \int_{\Sset_1} \widetilde{P}_{\nu,r}(x;\Sset_2) \,d\widetilde{\pi}_{\nu,r}(x).
\end{equation*}
The uniform continuous normalized cut and conductance are then
\begin{equation*}
\widetilde{\Phi}_{\nu,r}(\Sset) := \frac{\widetilde{Q}_{\nu,r}(\Sset, \Sset^c)}{\min\set{\widetilde{\pi}_{\nu,r}(\Sset),\widetilde{\pi}_{\nu,r}(\Sset^c)}}, \quad \widetilde{\Phi}_{\nu,r} := \min_{\Sset \subseteq \mc{C}_{\sigma}} \widetilde{\Phi}_{\nu,r}(\Sset),
\end{equation*}
where the minimum is taken over all measurable sets $\Sset \subseteq \mc{C}_{\sigma}$.

\begin{lemma}
	\label{lem: uniform_continuous_conductance}
	Let $\mc{C}_{\sigma}$ satisfy Assumption \textcolor{red}{(A3)} (of our main document) for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \mc{C}_{\sigma}$ with Lipschitz constant $L$. Let $0 < \ell < 1/2$ be a number that satisfies $\ell_{\nu,r}(x) \geq \nu_d r^d \ell$ for all $x \in \mc{C}_{\sigma}$.  Then the uniform conductance $\widetilde{\Phi}_{\nu,r}$ is lower bounded:
	\begin{equation*}
	\widetilde{\Phi}_{\nu,r} \geq \Bigl(1 - \frac{r}{4\rho}\Bigr) \cdot\frac{\ell^2\sqrt{2\pi}}{9} \cdot \frac{r}{\rho L \sqrt{d + 2}}
	\end{equation*}
\end{lemma}
Lemma~\ref{lem: overlap_balls} gives the lower bound $\ell \geq 1/2 \cdot (1 - r/\sigma \cdot \sqrt{(d + 2)/(2\pi)})$ leading to the following corollary.
\begin{corollary}
	\label{cor: uniform_continuous_conductance}
	Let $\mc{C}_{\sigma}$ satisfy Assumption \textcolor{red}{(A3)} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \mc{C}_{\sigma}$ with Lipschitz constant $L$. Then the uniform conductance $\widetilde{\Phi}_{\nu,r}$ is lower bounded:
	\begin{equation*}
	\widetilde{\Phi}_{\nu,r} \geq \Bigl(1 - \frac{r}{4\rho}\Bigr) \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r}{\rho L \sqrt{d + 2}}
	\end{equation*}
\end{corollary}
